Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-01 sections/tensors.tex
Update on Overleaf.

\teo{Here is a new paragraph.}
In the rest of this section, we describe this functionality in detail after we review the basics of level abstractions~\cite{sze2017efficient,chou2022compilation, chou2018format}.
%
Then we discuss $declare$, $freeze$, $thaw$, and $unfurl$ functions as part of a life cycle abstraction as well as the $assemble$ function.
%
These interfaces add to the level abstraction, expanding the types of data that they can express via mapping to Looplets and expanding the contexts in which they can be used.
%
Finally, we describe several levels that we implement in this abstraction, which allow us to implement our taxonomy of known structures.

>>>>

\teo{Here is a new paragraph.}
In the rest of this section, we describe this functionality in detail after we review the basics of level abstractions~\cite{sze2017efficient,chou2022compilation, chou2018format}.
%
Then we discuss $declare$, $freeze$, $thaw$, and $unfurl$ functions as part of a life cycle abstraction as well as the $assemble$ function.
%
These interfaces add to the level abstraction, expanding the types of data that they can express via mapping to Looplets and expanding the contexts in which they can be used.
%
Finally, we describe several levels that we implement in this abstraction, which allow us to implement a taxonomy of known structures that appear in tensor computations.
